Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of G dwarfs

### 2017-08-03 paper/ms.tex
Fix spectral types
back

\documentclass[12pt,letterpaper,margin=1in]{article}
% \documentclass[twocolumn]{aastex61}

@@

% packages
\usepackage[letterpaper,margin=1in]{geometry}

\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage[sort&compress,super]{natbib}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{aas_macros}
\usepackage{hyperref}
\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
\usepackage{mathptmx}
\usepackage{threeparttable}

% per section figure counting
\usepackage{chngcntr}
\counterwithin{figure}{section}

%\setcitestyle{super}
\citestyle{nature}
\bibliographystyle{naturemag}

@@

\newcommand{\todo}[1]{{\color{red}TODO: #1}}

@@

% Titles:
% - 90 characters (including spaces)
% - do not normally include numbers, acronyms, abbreviations or punctuation
% - They should include sufficient detail for indexing purposes but be general
%   enough for readers outside the field to appreciate what the paper is about.
\title{
\vspace{-2cm}
  Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars
  \vspace{-0.5cm}
}

\author{
  Semyeong Oh$^{1,*}$,\,
  Adrian M. Price-Whelan$^{1}$,\,
  John M. Brewer$^{2,3}$,\,\\
  David W. Hogg$^{4,5,6,7}$,\,
  David N. Spergel$^{1,4}$,\,
  Justin Myles$^{2}$
}
\date{\small\today}

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me
\maketitle

% affiliations
\vspace{-1cm}
{\small\noindent
  $^1$Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA \\
  $^2$Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA \\
  $^3$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA \\
  $^4$Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA \\
  $^5$Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA \\
  $^6$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA \\
  $^7$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg \\
  $^*$To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}
}

%% \author{Keith A. Hawkins}
%% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}

%% \author{Nathan W. C. Leigh}
%% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}

% ------------------------
% nature summary paragraph
% ------------------------
% - a fully referenced paragraph, ideally of about 200 words, but certainly no
%   more than 300 words, aimed at readers in other disciplines.
% - This paragraph starts with a 2-3 sentence basic introduction to the field;
%   followed by a one-sentence statement of the main conclusions starting 'Here
%   we show' or equivalent phrase; and finally, 2-3 sentences putting the main
%   findings into general context so it is clear how the results described in
%   the paper have moved the field forwards.
% - annotated example: https://www.nature.com/nature/authors/gta/2c_Summary_para.pdf
% ------------------------
\section{Summary}
{\bf \noindent
  Stars that are born together are expected to have the same chemical
  compositions initially.
  Detailed chemical abundance studies of stars in wide binaries indeed reveal
  little to no abundance differences in most
  cases\citep{Gratton:2001aa,Desidera:2004aa}.
  However, the formation and evolution of different planetary systems around
  each star in a wide binary may eventually lead to differences in the chemical
  abundances of the component stars' radiative and convective
  layers\cite{Pinsonneault:2001aa,Chambers:2010aa}.
  Wide binary systems of two twin-like stars are particularly useful since such
  chemical signature may be more easily detectable as abundance differences,
  free from dependences on stellar parameters or confusion with Galactic
  chemical evolution.
  A handful of wide binaries that show small differences ($0.03$--$0.1$~dex)
  in their surface chemical abundances have been reported so far
  \cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,Teske:2013aa,
    Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa},
  however, a conclusive example of planetary accretion has not yet been found.
  %
  Here we report the discovery of a comoving pair of bright, sun-like
  stars---HD~240430 and HD~240429, hereafter ``\bizarreone'' and
  ``\sunanalog''--- with significant differences ($\approx 0.2$~dex) in their
  chemical abundances that strongly suggest accretion of a massive rocky
  planetary system in one of the stars within the last billion years.
  The more metal-rich of the two, \bizarreone, shows an enhancement of refractory
  elements by $\approx 0.2$~dex and a small enhancement ($\lesssim 0.11$~dex) of
  (moderately) volatile elements.
  The two stars also show high \elem{Li} abundance given their age of $\sim 4$ Gyr,
  as inferred from their stellar parameters.
  We suggest that the star \bizarreone\ accreted
  $\approx 15$~\mearth\ of rocky material, selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star, \sunanalog, may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  This pair of stars provides evidence that dynamical accretion of rocky planets
  does happen during the main-sequence lifetime of sun-like stars.
}

\section{Main Text}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair,
    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet much less in
    \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
    \label{fig:abundances}
  }
\end{figure}

\begin{table*}[htpb]
  \centering
  \begin{threeparttable}
  \caption{Astrometric and spectroscopic measurements of the pair\label{tab:t1}}
\begin{tabular}{ccccc}
\hline\hline
                        &                & \sunanalog\            & \bizarreone\           &               \\
Name                    & Units          & HD 240429              & HD 249439              & Uncertainties \\
\hline
Sp Type                 &                & G2                     & G0                     &               \\
R.A.\tnote{a}           & hh:mm:ss       & 23:51:55.21            & 23:52:09.42            &               \\
Dec.\tnote{a}           & dd:mm:ss       & 59:42:48.16            & 59:42:26.08            &               \\
2MASS $J$\tnote{a}      & mag            & $8.593 \pm 0.023$      & $8.415 \pm 0.026$      &               \\
$T_\mathrm{eff}$        & K              & 5878                   & 5803                   & 25            \\
$\log{g}$               &                & 4.43                   & 4.33                   & 0.028         \\
$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    & 0.5           \\
$[\elem{Fe}/\elem{H}]$  &                & 0.01                   & 0.20                   & 0.010         \\
Age\tnote{b}            & Gyr            & $4.00_{-1.56}^{+1.51}$ & $4.28_{-1.03}^{+1.11}$ &               \\
$v_r$                   & \kms\          & $-21.2$                & $-21.2$                & 0.2           \\
$\varpi$\tnote{a}       & mas            & $9.35 \pm 0.24$        & $9.41 \pm 0.25$        &               \\
$\mu_\alpha^*$\tnote{a} & mas\,yr$^{-1}$ & $89.25 \pm 0.66$       & $89.41 \pm 0.69$       &               \\
$\mu_\delta$\tnote{a}   & mas\,yr$^{-1}$ & $-29.68 \pm 0.54$      & $-30.12 \pm 0.52$      &               \\
\hline
\multicolumn{5}{c}{$T_c < 1200$~K} \\
\hline
$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 & 0.05          \\
$\elemH{C}$             &                & $0.00$                 & $0.09$                 & 0.026         \\
$\elemH{N}$             &                & $-0.06$                & $-0.01$                & 0.042         \\
$\elemH{O}$             &                & $0.01$                 & $0.09$                 & 0.036         \\
$\elemH{Na}$            &                & $-0.06$                & $-0.04$                & 0.014         \\
$\elemH{Mn}$            &                & $-0.03$                & $0.00$                 & 0.020         \\
\hline
\multicolumn{5}{c}{$T_c > 1200$~K} \\
\hline
$\elemH{Mg}$            &                & $0.01$                 & $0.19$                 & 0.012         \\
$\elemH{Al}$            &                & $0.01$                 & $0.21$                 & 0.028         \\
$\elemH{Si}$            &                & $0.00$                 & $0.16$                 & 0.008         \\
$\elemH{Ca}$            &                & $0.02$                 & $0.23$                 & 0.014         \\
$\elemH{Ti}$            &                & $0.02$                 & $0.20$                 & 0.012         \\
$\elemH{V}$             &                & $0.02$                 & $0.20$                 & 0.034         \\
$\elemH{Cr}$            &                & $0.01$                 & $0.17$                 & 0.014         \\
$\elemH{Fe}$            &                & $0.01$                 & $0.20$                 & 0.010         \\
$\elemH{Ni}$            &                & $-0.01$                & $0.21$                 & 0.014         \\
$\elemH{Y}$             &                & $0.04$                 & $0.26$                 & 0.030         \\
\hline
\end{tabular}
\begin{tablenotes}
\item [a] From \tgas.
\item [b] Derived in this work by isochrone fitting using the Yale-Yonsei model
  isochrones\cite{2013ApJ...776...87S}.
\item [c] Absolute abundances from Myles \etal\ (in prep.).
%\item All values are from \citet{2016ApJS..225...32B} unless otherwise noted.
\end{tablenotes}
\end{threeparttable}
\end{table*}

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).
The abundances are noted as \elemH{X}, defined as the log ratio of number
density of element \elem{X} to \elem{H} relative to the solar value
($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
\log_{10} (n_\elem{Li}/n_\elem{H})$.

% likely origin given its proximity in phase space
The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
and the maximum-likelihood 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties,
confirming that they are truly comoving (\sectionname~\ref{supp:dxdv}).
As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
\sunanalog\ are likely a coeval, bound wide-binary system.

% coevality based on stellar parameters
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with effective temperature, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (\figname~\ref{fig:yyisofitting}).

% metallicity and abundance difference
However, one of the stars, \bizarreone, is significantly more metal rich than
the other by 0.2~dex in \feh\ ($\approx 60\%$ in number density;
\figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of spectral
data and model between the two stars show significant residuals of almost all
metal line features, largely dominated by \elem{Fe}.
However, for absorption lines of elements that are not as enhanced in
\bizarreone\, the residuals are much smaller in amplitude demonstrating the
validity of the measured abundance differences (\figname~\ref{fig:spec1},
\ref{fig:spec2} and \ref{fig:spec_lithium}).

% novelty
The observed difference in metallicity and abundances is genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K)
wide-binary pairs examined using spectra of similar quality and the same
consistent measurement procedure shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
In fact, the abundance pattern of \bizarreone\ is very unusual
for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
implying that a scenario involving Galactic chemical evolution is not plausible
even if we ignore the coeval comparison star, \sunanalog.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(\figname~\ref{fig:relabun_tcrank}).

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
burning. %TODO: REFERENCE?
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (\figname~\ref{fig:spec_lithium}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference (blue circles) to the expected
    change in solar surface abundance after adding $15$~\mearth\ of material
    with bulk Earth composition\cite{2003TrGeo...2..547M} (black open and
    filled circles).
    The assumed mass fraction in the convective zone is $0.02$.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas on the $x$-axis.
    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
    in filled circles, while those without a measurement are left open.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $15$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated in the inset.
  }
  \label{fig:deltaxh_tcrank}
\end{figure}

>>>>

\documentclass[modern, letterpaper]{aastex61}
% \documentclass[twocolumn]{aastex61}

@@

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}
\bibliographystyle{aasjournal}

@@

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}

@@

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing % trust me

\title{
  Kronos \& Krios:
  Evidence for accretion of a massive, rocky planetary system
  in a comoving pair of G dwarfs
}

\author[0000-0001-7790-5308]{Semyeong Oh}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
  Princeton, NJ 08544, USA}
\affil{To whom correspondence should be addressed: \texttt{semyeong@astro.princeton.edu}}

\author[0000-0003-0872-7098]{Adrian M. Price-Whelan}
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
  Princeton, NJ 08544, USA}

\author[0000-0002-9873-1471]{John M. Brewer}
\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
  New Haven, CT 06511, USA}

\author[0000-0003-2866-9403]{David W. Hogg}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
  New York, NY 10010, USA}
\affil{Center for Cosmology and Particle Physics,
  Department of Physics, New York University, 726 Broadway,
  New York, NY 10003, USA}
\affil{Center for Data Science, New York University, 60 Fifth Ave,
  New York, NY 10011, USA}
\affil{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg}

\author{David N. Spergel} % TODO: need ORCID
\affil{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane,
  Princeton, NJ 08544, USA}
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave,
  New York, NY 10010, USA}

% \author{Keith A. Hawkins}
% \affil{Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA}

% \author{Nathan W. C. Leigh}
% \affil{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}

\author{Justin Myles} % TODO: need ORCID
\affil{Department of Astronomy, Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}

\begin{abstract}
  We report and discuss the discovery of a comoving pair of bright G
  stars, HD~240430 and HD~240429, with a significant difference in their
  chemical abundances.
  The two stars have an estimated separation of $\approx 0.6$~pc at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocities,
  %($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence),
  as inferred from \gaia\ \tgas\ parallaxes and proper motions, and
  high-resolution radial velocity measurements.
  Stellar parameters determined from high-resolution Keck HIRES spectra
  indicate that both stars are $\sim 4$~Gyr old,
  yet both stars show very high surface \elem{Li} abundance for this age.
  The more metal-rich of the two, HD~240430, shows an enhancement of refractory
  ($\Tcondens>1200$~K) elements by $\approx 0.2$~dex but not as large
  an enhancement of (moderately) volatile elements ($\Tcondens<1200$~K; \elem{C},
  \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}).
  This is the largest and the most significant chemical difference found in
  a wide binary pair yet.
  The proximity in phase-space and ages between the two stars suggests that
  they formed together with the same composition, at odds with the observed
  differences in metallicity and abundance patterns.
  We therefore suggest that the star HD~240430, ``Kronos'', recently accreted
  $\approx 20$~\mearth\ of rocky material after birth selectively enhancing the
  refractory elements in its surface and convective envelope.
  The other star HD~240429, ``Krios'', may also have had a similar accretion
  event given its high surface \elem{Li} abundance but of much smaller amount
  ($\approx 4$~\mearth).
  %Follow-ups to study the existence and properties of the planetary systems
  %around these stars will help illuminate planet-star interactions.
\end{abstract}

\keywords{
  binaries: visual
  ---
  planet-star interactions
  ---
  stars: abundances
  ---
  stars: formation
  ---
  stars: individual (HD~240430, HD~240429)
  ---
  stars: solar-type
}

\section{Introduction} % (fold)
\label{sec:introduction}

Wide binary stars are valuable tools for studying star and planet formation as well
as Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by, e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
For example, the separation distribution of halo binaries has been used to
constrain the mass of massive compact halo objects (\citealt{Yoo:2004aa}).
On the other hand, they are also prime targets to test the chemical tagging
hypothesis that stars from the same birthplace may be traced back using detailed
chemical abundance patterns as birth ``tag''s (\citealt{2002ARA&A..40..487F}).
A multiple-star system of any size that we believe are born together can serve
this purpose, with massive open clusters at one extreme.
Wide binaries are at the other extreme in that we may be less confident of the
coevality of individual systems but they are much more abundant than larger
systems like open clusters, rendering their statistics a meaningful indication
of whether the hypothesis works.

Wide binaries with similar or very different planetary architectures around the
component stars have been used to connect a host star's chemistry to its
planetary system.
A differential analysis may reveal chemical signatures related to planet
formation or accretion without any regard to Galactic chemical evolution as
long as the two stars are assumed to be born together with identical
composition.
For close-in giant planets, it has been established that the planet-metallicity
relation is primordial, and that the enhanced metallicity in giant
planet-hosting stars likely promotes the formation of giant planets by
increasing the availability of small particle condensates that form
planetesimals (\citealt{Fischer:2005aa}).
On the other hand, if host stars are polluted after their birth by rocky
planetary material with high refractory-to-volatile ratio, the convective
envelope of the stars may be enhanced in refractory elements (e.g., \elem{Fe})
compared to their initial state.
Thus, differences in planet formation or accretion in two otherwise identical
stars may imprint differences in chemical abundances that depend on the
condensation temperature (\Tcondens).

Several systems in which at least one star hosts at least one planet
have been studied so far with high resolution spectroscopy in this context
(\citealt{Teske:2013aa,Mack:2014aa,Liu:2014aa,Teske:2015aa,Saffe:2015aa,
  Ramirez:2015aa,Biazzo:2015aa,Mack:2016aa,Teske:2016aa,Teske:2016ab}).
The results and interpretations of these studies are varied:
while some systems appear to have undetectable differences
(see also \citealt{Desidera:2004aa,Gratton:2001aa}), other
studies have reported a \Tcondens-dependent difference in abundance
with higher-\Tcondens\ elements showing larger differences.
The increasing abundance difference with condensation temperature has been
attributed both to more yet-undiscovered rocky planets around the relatively
refractory-poor star and to late time accretion of refractory-rich planetary
material (\citealt{Ramirez:2015aa,Biazzo:2015aa}).
The observed differences are $\lesssim 0.1$~dex even in the most dramatic case,
and often at $\approx 0.05$~dex level making them challenging to detect even
with a careful analysis of high-resolution high signal-to-noise ratio spectra.
% maybe want to point out the former interpretation roots back to melendez+09
% and some doubt to that interpretation...

So far the strongest evidence for accretion of planetary material by a host
star comes from spectral analysis of polluted white dwarfs (WDs).
Because the gravitational settling times of elements heavier than \elem{He} in
atmosphere is much shorter than the WD cooling time, detection of metals likely
indicates the presence of a reservoir of dusty material around the WD.
Indeed, many of the polluted WDs host a dusty debris disk detected
in the infrared.
Some of the most dramatically polluted WDs show
surface abundances closely matched by rocky planetary material
with, e.g., bulk Earth composition, strongly arguing
that the disk formed from tidally disrupted minor planets
(\citealt{Zuckerman:2007aa,Klein:2010aa}).
Recently, transit signals from small bodies orbiting around a polluted WD
have been detected by \project{Kepler} adding further support to the picture
(\citealt{2015Natur.526..546V}).

Here, we report and discuss the discovery of a comoving pair of G stars,
HD~240430 and HD~240429, with unusual chemical abundance differences
that strongly suggest accretion of planetary material by the two stars.
Throughout the \documentname, we nickname the two stars \bizarreone\
(HD~240430) and \sunanalog\ (HD~240429).
We use the following convention for chemical abundances of stars: \elemH{X} is
the log ratio of number density of element \elem{X} to \elem{H} relative to the
solar value.
The absolute abundance of \elem{X} is $A(\elem{X}) = 12 + \log_{10}
(n_\elem{X}/n_\elem{H})$ where $n_\elem{X}$ is the number density of element
\elem{X}.
In \sectionname~\ref{sec:data} we present the astrometric and spectroscopic data
about the two stars relevant to the present discussion.
In \sectionname~\ref{sec:discussion} we discuss possible interpretations of
the abundance difference between the pair.
We summarize our discussions in \sectionname~\ref{sec:summary}.

\subsection{Review of Detailed Chemical Abundance Studies of Wide Binary Stars}
\label{sub:review}

Anticipating the forthcoming discussion, we review and summarize a handful of
wide binary systems that have been studied in
their detailed chemical abundances so far with high-resolution spectroscopy.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
We focus on key characteristics of stars and planets, and interpretations of
any trend in $\Delta\elemH{X}$ with \Tcondens.
(\todo{smoh: discussion of HD~1333131AB and 16 Cyg is missing, but will be added})

{\bf HD~20782/HD~20781:}
Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$).\footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}
The measured abundances of 15 elements in the two stars are consistent
(\citealt{Mack:2014aa}).
However, \citealt{Mack:2014aa} argued that there is a moderately significant
($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
the abundances of each star {\it individually}.
They suggest that this slope is evidence that the stars accreted
$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
migration.

{\bf HAT-P-1:}
A pair of G0 stars separated by 11\arcsec\ with $\feh\approx0.15$ has
different planetary systems:
the secondary star is known to host one transiting giant planet
while no planet has been discovered around the primary star.
The two stars are identical
in metallicities and abundances for 23 elements measured with
the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
Thus it seems that the presence of close-in giant planet does not necessarily
lead to atmospheric pollution of its host star.

{\bf HD~80606/HD~80607:}
Similar to HAT-P-1, no significant chemical difference is found between two
common proper motion G5 stars with super-solar metallicity ($\feh \approx
0.35$): HD~80606 which hosts a very eccentric ($e\approx0.94$) giant planet and
HD~80607 which has no detected planets (\citealt{Saffe:2015aa,Mack:2016aa}).

{\bf XO-2N/XO-2S:}
A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$)
has received much attention due to possibly the most robust and significant
difference between the component stars.
XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
0.15$) orbits at $<0.5$~AU.
%TODO: check following with Biazzo+
All measured elements including \elem{Fe} are enhanced in XO-2N relative to
XO-2S, and the difference shows a significant correlation with \Tcondens\
(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
\citealt{Teske:2013aa}).
At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
difference spans upto $0.1$~dex at $\Tcondens>1600$~K.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelope of the
host star, they can match the mass difference of gas giant planets around each
star, which is at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
opposite would be true.

{\bf WASP-94A/WASP-94B:}
Each star in a pair of F8 and F9 stars with super-solar metallicity
($\feh\approx 0.3$) hosts a hot Jupiter.
The planet around WASP-94A is transiting with a misaligned, probably retrograde
circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
uncertainty of $0.006$~dex among all elements
resulting in a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
  %TODO: double check the following statement
  Note that the condensation
  temperature $\Tcondens$ used is for solar system composition
  gas, which can differ from that of higher metallicity gas.}
Multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars were considered, but none was favored.

\section{Data}
\label{sec:data}

\input{kk.tex}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1}
    but for smaller portions of spectra at longer wavelengths that are
    not dominated by \elem{Fe}.
    We mark elements that give rise to strong absorption lines.
    The feature in the third column of the second row is a strong \elem{Li}
    line that was not modeled by \citealt{2016ApJS..225...32B}; this line was
    studied in a separate work (\citealt{jmlithium}).
    Note that the lines of \elem{Na} and \elem{O}, which are under-enhanced
    in \bizarreone\ relative to \elem{Fe} or other refractory elements,
    show weaker residuals.
  }
  \label{fig:spec2}
\end{figure}
